HyperLogLog: Exponentially Bad in Adversarial Settings

### 2021-08-28 docs/HLL_exp_bad/main.tex
switching to IEEE foramt, adding flags for preprint and anonymity

\newif\ifacmversion % turn on ACM style (can be short or full)
\acmversiontrue

\newif\ifanon % turn on ACM style (can be short or full)
\anonfalse

\ifacmversion

%\documentclass[sigconf, anonymous, dvipsnames]{acmart} %dvipsnames for old/new macros
\documentclass[sigconf, dvipsnames]{acmart} %dvipsnames for old/new macros

\fancyhf{} % Remove fancy page headers 
%\fancyhead[C]{Anonymous submission \#147 to ACM CCS 2021} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
%\acmConference[Anonymous Submission to ACM CCS 2021]{ACM Conference on Computer and Communications Security}{Due 6 May 2021}{Seoul, South Korea}
%\acmYear{2021}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained

\else
\documentclass[%
	dvipsnames,	%% xcolor
	draft,
]{article}
\fi

\usepackage{graphicx, amsmath, amsthm, amssymb, setspace, array, url, hyperref, xspace, todonotes, pifont}
%\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

%\newtheorem{lemma}{Lemma}
%\newtheorem{theorem}{Theorem}

@@

\author{Kenneth G. Paterson}
%\orcid{...}
\affiliation{ETH Zurich}
\email{kenny.paterson@inf.ethz.ch}

\author{Mathilde Raynal}
%\orcid{...}
\affiliation{EPFL}
\email{mraynal@student.ethz.ch}

@@

@@

>>>>

\newif\ifIEEEversion % turn on IEEE style 
\IEEEversionfalse
\newif\ifanon % needed for acks, suppression of authors, etc
\anonfalse

\ifIEEEversion
%% what follows is for the IEEEtran format required for IEEE Euro S&P

\documentclass[compsoc,conference,a4paper,10pt,times]{IEEEtran}

%% our own choice of packages 
\usepackage{graphicx, amsmath, amsthm, amssymb, setspace, array, url, xspace, todonotes, pifont} %hyperref is supplied by IEEEtran below
%\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

%% packages and whatnot inherited from IEEEtran example file

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{bmpsize}
\usepackage{xcolor}
\usepackage{lipsum}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}
%% commented out this nonsense
%\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%   T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%% need these for IEEEtran - not defined in cls file
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

@@

\ifanon %% suppress authors in anonymous version
\author{}
\else
\author{\IEEEauthorblockN{Kenneth G. Paterson}
\IEEEauthorblockA{\textit{ETH Zurich} \\
kenny.paterson@inf.ethz.ch}
\and
\IEEEauthorblockN{Mathilde Raynal}
\IEEEauthorblockA{\textit{EPFL} \\
mraynal@student.ethz.ch}
}
\fi %end anon processing of authors

\else  %% what follows is a vanilla format for posting on eprint

\documentclass[a4paper,10pt]{article}

%% our own choice of packages 
\usepackage{graphicx, amsmath, amsthm, amssymb, setspace, array, url, xspace, todonotes, pifont, hyperref} 
\usepackage{a4wide}
%\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

@@

\title{HyperLogLog: Exponentially Bad in Adversarial Settings}
\ifanon %% suppress authors in anonymous version
\author{}
\else
\author{Kenneth G. Paterson\\ETH Zurich\\\texttt{kenny.paterson@inf.ethz.ch} \and Mathilde Raynal\\EPFL\\\texttt{mraynal@student.ethz.ch}}
\fi % end anon processing of authors 
\fi % end of vanilla format

@@

%\begin{IEEEkeywords}
%yadda yadda
%\end{IEEEkeywords}
